Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2023-04-03 Manuscript/manuscript.tex
Abstract now ~190 words, included contributions of this paper

%Abstract should be 200 words
%Devon Allen was disqualified in 2022... discussions about dq, talk methods and 
%models, venue effect, and conclusion
\begin{abstract}
  At the 2022 World Track Championships in Eugene Oregon, Devon Allen was disqualified in the
  Men's 110 meter hurdle final after registering a reaction time of 0.099 seconds, 0.001 
  seconds faster than what is allowed.  Following the games, bloggers on the running website 
  LetsRun scrutinized the results and performed non-statistical analysis of the data.
  They found that the reaction time data from the 2022 World Track Championships seemed to be faster 
  compared to the other datasets they looked at, but did not perform any meaningful statistical 
  analysis of the data.  Devon Allen had previously run the third-fastest time in history when 
  he ran 12.84 earlier in 2022 and was considered to be one of the favorites to win.  His 
  disqualification thus prompted questions into whether the timing equipment used at the World
  Track Championships was accurate and whether Allen actually reacted as fast as the 
  timing equipment stated he did. This paper questions the reaction time disqualification barrier, which is
  currently 0.1 seconds to determine whether this is a reasonable threshold as
  well as look at data that calls into question whether the timing equipment
  used at the 2022 Track and Field World Championships was faulty.
  There is little at this point that could be done to rectify any potential 
  mis-disqualification other than to try to prevent it from happening again.  
  This matter needs to be addressed because Devon Allen's disqualification could 
  be a problem that could continue to re-appear.  If athletes
  are reacting fast enough that the timing system thinks that they are reacting
  illegally fast, then World Athletics needs to address this and possibly change
  the minimum reaction time allowed.

>>>>

%Abstract should be 200 words
%Devon Allen was disqualified in 2022... discussions about dq, talk methods and 
%models, venue effect, and conclusion
\begin{abstract}
  Devon Allen was disqualified in the Men's 110 meter hurdle final of the 2022
  Track and Field World Championships after registering a reaction time of 0.099 seconds, 0.001 
  seconds faster than what is allowed.  Following the games, bloggers on the running website 
  LetsRun scrutinized the results and performed non-statistical analysis of the data.
  They found that the reaction time data from the 2022 World Track Championships seemed to be faster 
  compared to the other datasets they looked at, but did not perform any meaningful statistical 
  analysis of the data.  This paper questions the reaction time disqualification barrier, which is
  currently 0.1 seconds to determine whether this is a reasonable threshold.
  We employ a generalized linear mixed model (GLMM) with a random effect term
  which will be referred to as the venue effect in order to try and model the
  data.  Additionally, we employ a signed-rank test for clustered data to compare
  reaction times for the same athletes at different competitions.
  This matter needs to be addressed because Devon Allen's disqualification could 
  be a problem that could continue to re-appear in future world championships.
